---
title: "Frequent Pattern Growth Algorithm Solver"
output: html_notebook
---

#### Application Example.
|Transaction Id|Items|
|:------------:|:---:|
|T1|{E,K,M,N,O,Y}|
|T2|{D,E,K,N,O,Y}|
|T3|{A,E,K,M}|
|T4|{C,K,M,U,Y}|
|T5|{C,E,I,K,O,O}|

* __The above-given data is a hypothetical dataset of transaction with each letter representing an item.__
* __Let the minimum support be 3.__


```The frequent of each individual item is computed:```

|Item|Frequency|
|:----:|:---------:|
|A|1|
|c|2|
|D|1|
|E|4|
|I|1|
|K|5|
|M|3|
|N|2|
|O|3|
|U|1|
|Y|3|


_A_ __Frequent Pattern Set__ is build which will contain all the elements whose frequency is greater than or equal to the ___minimum support___.

___As minimum support be 3___
These elements are store in descending order of their respectif frequencies.
After insertion of the relevant items, the set L looks like :

> __L={K:5,E:4,M:3,O:3,Y:3}__.

Now, for each transaction, the respective __Ordered-Item set__ is build

> __Frequent Pattern set L={K:5,E:4,M:3,O:3,Y:3}__.

|Transaction Id|Items|Ordered-Item Set|
|:------------:|:---:|:--------------:|
|T1|{E,K,M,N,O,Y}|{K,E,M,O,Y}|
|T2|{D,E,K,N,O,Y}|{K,E,O,Y}|
|T3|{A,E,K,M}|{K,E,M}|
|T4|{C,K,M,U,Y}|{K,M,Y}|
|T5|{C,E,I,K,O,O}|{K,E,O}|



```{r}
#library(rCBA)
#install.packages("rCBA")
library("rCBA")
data("iris")

train <- sapply(iris,as.factor)
train <- data.frame(train, check.names=FALSE)
txns <- as(train,"transactions")

rules = rCBA::fpgrowth(txns, support=0.03, confidence=0.03, maxLength=2, consequent="Species",
           parallel=FALSE)

predictions <- rCBA::classification(train,rules)
table(predictions)
sum(as.character(train$Species)==as.character(predictions),na.rm=TRUE)/length(predictions)

prunedRules <- rCBA::pruning(train, rules, method="m2cba", parallel=FALSE)
predictions <- rCBA::classification(train, prunedRules)
table(predictions)
sum(as.character(train$Species)==as.character(predictions),na.rm=TRUE)/length(predictions)
```


```{r}
install.packages("r-shiny")
```
